\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-23 paper.tex
..

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth under network scenario $\mathbf{z}$ to the demanded bandwidth, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
$\mathbf{z} \propto <d, \{f_d^t\}> \quad \Leftrightarrow \quad \forall k, R_{dk}^{\mathbf{z}} \ge 1$. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle a linear programming problem.

>>>>

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth under network scenario $\mathbf{z}$ to the demanded bandwidth, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
$\mathbf{z} \propto <d, \{f_d^t\}> \quad \Leftrightarrow \quad \forall k, R_{dk}^{\mathbf{z}} \ge 1$. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle the following linear programming problem.
